Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-03-07 ProbabilisticCoherence.tex
Updated section 4

@@

\begin{definition}\label{def:reconpoint}
  Let $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$, and let 
  \begin{equation}
    \tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h}),
  \end{equation} 
  where $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m$. Then $\tilde{\bm{y}}_{t+h}$ is said to be ``reconciled'' if  $\tilde{\bm{y}}_{t+h} \in \mathbb{C}^m$, where $\bm{S}\circ \bm{g}(.)$ is a projection of $\bm{g}(.)$ onto $\mathbb{C}^m$.
\end{definition}

The importance of Definition \ref{def:reconpoint} is that it allows for both linear and non-linear reconciliation. In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear. On the other hand, if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(.)$ will linearly projects incoherent point forecasts onto $\mathbb{C}^m$. Latter was the main focus in previous studies in hierarchical point forecasting, where $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.

In the following content we provide an alternative explanation for linear reconciliation based on definition (\ref{def:reconpoint}). Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ consists the columns that spans $\bm{\mathbb{N}}^{n-m}$ which is orthogonal to $\mathbb{C}^m$. Note that $\bm{R}$ is also not unique and one example is a matrix whose columns represent the aggregation constraints for a given hierarchy. Then for the hierarchy in example 1, 
$$ 
\bm{S} = 
\begin{pmatrix} 
1& 1 \\ 1 & 0 \\ 0&1 
\end{pmatrix} 
\quad \text{and} \quad 
\bm{R} = 
\begin{pmatrix}  
1 \\ -1 \\ -1 
\end{pmatrix}.
$$

Further let $\{\bm{s}_1,...,\bm{s}_m\}$ and $\{\bm{r}_1,...,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,...,\bm{s}_m, \bm{r}_1,...,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of definition (\ref{def:reconpoint}), we can use the following steps to reconcile the point forecasts.

@@

For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$. Let $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}'$ denote these coordinates. Note that $\tilde{\bm{b}}_{t+h}$ is a basis series which is really the reconciled bottom level series that corresponds to the coefficients of linear combination of the basis $\{\bm{s}_1,...,\bm{s}_m\}$. Similarly, $\tilde{\bm{t}}_{t+h}$ is another basis series corresponds to the coefficients of linear combination of the basis $\{\bm{r}_1,...,\bm{r}_{n-m}\}$. Then from basic properties of linear algebra it follows that,

\[
\begin{pmatrix}
\bm{S} & \vdots& \bm{R}
\end{pmatrix}
\begin{pmatrix}
\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}
\end{pmatrix}'
= \hat{\bm{y}}_{t+h},
\]
\[
\hat{\bm{y}}_{t+h} = \bm{S}\tilde{\bm{b}}_{t+h} +  \bm{R}\tilde{\bm{t}}_{t+h},
\]
and
\begin{equation}\label{4.3}
\begin{pmatrix}
\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}
\end{pmatrix}' =
\begin{pmatrix}
\bm{S} & \vdots& \bm{R}
\end{pmatrix}^{-1}
\hat{\bm{y}}_{t+h}.
\end{equation}

In order to find $\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
respectively. Then $\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}$ is given by,
\begin{equation}
\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
\end{pmatrix}.
\end{equation}
Thus we have,
\begin{equation} \label{4.4}
\begin{pmatrix}
\tilde{\bm{b}}_{t+h} \\ \cdots \\ \tilde{\bm{t}}_{t+h}
\end{pmatrix} = \begin{pmatrix}
(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
\end{pmatrix}\hat{\bm{y}}_{t+h}.
\end{equation}

@@

This step directly follows by the definition for coherent forecasts. That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \mathbb{R}^n$ to the $\mathbb{C}^m$ through $\bm{S}$. Thus we have, 
\begin{equation}
\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathbb{C}^m<\mathbb{R}^n.
\end{equation}

Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will result optimally reconciled point forecasts of the hierarchy. Notice that, if $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.

Further in our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible. i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$. This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.

In their study, \citet{Hyndman2011} proposed to choose,
\begin{equation*}
\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
\end{equation*}
where in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy is given by,
\begin{equation}
\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
\end{equation}
They referred this to as OLS solution and the loss function they considered is equivalent to the euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$, i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.

According to a recent study by \citet{Wickramasuriya2017}, choosing $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness where, $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors. This will result,
\begin{equation*}
\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}'\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
\end{equation*}
and thus,
\begin{equation}
\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
\end{equation}

They referred this to as MinT solution. It is also worth to notice that the loss function they considered is equivalent to the Mahalanobis distance between $\hat{\bm{y}}_{T+h}$ and $\tilde{\bm{y}}_{T+h}$. i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>_{\bm{W}_h}$.

@@

In terms of probabilistic forecasts, the reconciliation implies finding the probability measure of the coherent forecasts using the information of incoherent probabilistic forecast measure. A more formal definition is given below.

\begin{definition} \label{def:reconprob}
  Suppose $(\mathbb{R}^n, \mathscr{F}^n, \hat{\nu})$ be an incoherent probability triple and $(\mathbb{R}^m, \mathscr{F}^m, \nu^m)$ be a probability triple defined on $\mathbb{R}^m$. Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $. Then the probability measure on reconciled bottom levels is such that,
  \begin{equation}
  \nu^m(\bm{A}) = \hat{\nu}(\bm{g}^{-1}(\bm{A})), \quad \forall \quad \bm{A} \in \mathscr{F}^m.
  \end{equation}

  Further the reconciled probability measure of the whole hierarchy is given by,
  \begin{equation}
  \tilde{\nu}(\bm{S}(\bm{A})) = \hat{\nu}(\bm{g}^{-1}(\bm{A})), \quad \forall \quad \bm{A} \in \mathscr{F}^m,
  \end{equation}
  where $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{C}^m$ and $\tilde{\nu}(.)$ is the probability measure on the measure space $(\mathbb{C}^m, \mathscr{F}_S)$.
\end{definition}

Since the above definition seems not to be straightforward in reconciling incoherent forecasts, the following content explains how this can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.

Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of that with respect to the basis $\bm{B}$ is given by \eqref{4.3}. Suppose $\hat{\bm{f}}(.)$ is the probability density of $\hat{\bm{y}}_{t+h}$. Our goal is to reconcile $\hat{\bm{f}}(.)$ such that the density lives on the $\mathbb{C}^m$. In order to obtain this reconciled density, we need to project $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ onto the $\mathbb{C}^m$ along the direction of $\mathbb{N}^{n-m}$.

Let the density of coordinates of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ is denoted by $\bm{f_B}(.)$. Then it follows from  \eqref{4.3} and the facts on density of transformed variables,
\begin{equation}\label{4.5}
\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big|,
\end{equation}
where $|.|$ denote the determinant of a matrix. Now that we have the density of $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' $, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating \eqref{4.5} over the range of $\tilde{\bm{t}}_{t+h}$. This will result the reconciled density of the bottom level series $\tilde{\bm{b}}_{t+h}$. i.e.,
\begin{equation}\label{4.6}
\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big| \quad d\tilde{\bm{t}}_{t+h}.
\end{equation}

Finally to get the reconciled density of the whole hierarchy, we simply follow the definition (\ref{def:cohprob}) and have,
\begin{equation}\label{4.7}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\bm{S}\circ \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h}).
\end{equation}
This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathbb{C}^m<\mathbb{R}^n$. Following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.

@@

Suppose $\mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \overset{d}{\leftrightarrow} \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$. Then from \eqref{4.5} it follows,

@@

\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big| = \frac{\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) }{\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}.

@@

By substituting the Gaussian distribution function to $\bm{f_B}(.)$ we get,

@@

\bm{f_B}(.)

@@

\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})' \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\

@@

\frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)' \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\

@@

\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
\exp \Big\{-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)'\\
& \hspace*{1cm} \Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}'\Big]^{-1}
\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.

@@

Recall that,

@@

\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} =

@@

where, $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{Q}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then,

@@

\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix} \Big|}

>>>>

\def\PQ{\begin{pmatrix}\bm{P}\\[-0.2cm]\bm{Q}\end{pmatrix}}
\def\bt{\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\[-0.2cm]\tilde{\bm{t}}_{t+h}\end{pmatrix}}

@@

\begin{definition}\label{def:reconpoint}
  Let $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$, and let 
  \begin{equation}
    \tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h}),
  \end{equation} 
  where $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m$ and $\bm{S}\circ \bm{g}(\cdot)$ is a projection of $\bm{g}(\cdot)$ onto $\mathbb{C}^m$. Then $\tilde{\bm{y}}_{t+h}$ is said to be ``reconciled'' if  $\tilde{\bm{y}}_{t+h} \in \mathbb{C}^m$.
\end{definition}

Definition \ref{def:reconpoint} allows for both linear and non-linear reconciliation. In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear, while if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(\cdot)$ will linearly project incoherent point forecasts onto $\mathbb{C}^m$. Previous studies in hierarchical point forecasting have only focussed on the linear case, $\bm{g}(\bm{y}) = \bm{P}\bm{y}$, where $\bm{P}$ is an $m \times n$ matrix, and so $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.

Using Definition \ref{def:reconpoint}, we can now explain previous results for linear forecast reconciliation. Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ comprise the columns that span $\bm{\mathbb{N}}^{n-m}$, which is orthogonal to $\mathbb{C}^m$. Note that $\bm{R}$ is not unique; one example is a matrix whose columns represent the aggregation constraints for a given hierarchy. For the hierarchy in example 1, 
$$ 
\bm{S} = 
\begin{pmatrix} 
1& 1 \\ 1 & 0 \\ 0&1 
\end{pmatrix} 
\quad \text{and} \quad 
\bm{R} = 
\begin{pmatrix}  
1 \\ -1 \\ -1 
\end{pmatrix}.
$$

Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of Definition \ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.

@@

For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$. Let $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$ denote these coordinates. Note that $\tilde{\bm{b}}_{t+h}$ is a basis series which is equivalent to the reconciled bottom level series, and which corresponds to the linear combination coefficients of the basis $\{\bm{s}_1,\dots,\bm{s}_m\}$. Similarly, $\tilde{\bm{t}}_{t+h}$ is another basis series corresponding to the linear combination coefficients of the basis $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$. Then from basic properties of linear algebra it follows that, 
\[
(\bm{S} ~ \vdots~ \bm{R})
(\tilde{\bm{b}}'_{t+h},~ \tilde{\bm{t}}'_{t+h})'
= \hat{\bm{y}}_{t+h},
\]
\[
\hat{\bm{y}}_{t+h} = \bm{S}\tilde{\bm{b}}_{t+h} +  \bm{R}\tilde{\bm{t}}_{t+h},
\]
and
\begin{equation}\label{4.3}
(\tilde{\bm{b}}'_{t+h}, ~ \tilde{\bm{t}}'_{t+h})' =
(\bm{S} ~ \vdots~ \bm{R})^{-1}
\hat{\bm{y}}_{t+h}.
\end{equation}

In order to find $(\bm{S} ~ \vdots~ \bm{R})^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
respectively. Then $(\bm{S} ~ \vdots~ \bm{R})^{-1}$ is given by,
\begin{equation}
(\bm{S} ~ \vdots~ \bm{R})^{-1} = \begin{pmatrix}
(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
\end{pmatrix}.
\end{equation}
Thus we have,
\begin{equation} \label{4.4}
\begin{pmatrix}
\tilde{\bm{b}}_{t+h} \\ \cdots \\ \tilde{\bm{t}}_{t+h}
\end{pmatrix} = \begin{pmatrix}
(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
\end{pmatrix}\hat{\bm{y}}_{t+h}.
\end{equation}

@@

This step directly follows from the definition for coherent forecasts. To obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \mathbb{R}^n$ to the $\mathbb{C}^m$ through $\bm{S}$. Thus we have, 
\begin{equation}
\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \qquad \tilde{\bm{y}}_{t+h} \in \mathbb{C}^m<\mathbb{R}^n.
\end{equation}

Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will lead to optimally reconciled point forecasts of the hierarchy. If $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.

In our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible; i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$. This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.

\citet{Hyndman2011} proposed to choose
\begin{equation*}
\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
\end{equation*}
where in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by,
\begin{equation}
\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
\end{equation}
They referred this to as the OLS solution and the loss function they considered is equivalent to the Euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$; i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.

According to a recent study by \citet{Wickramasuriya2017}, selecting $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness, where $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors. This will result in
\begin{equation*}
\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}'\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
\end{equation*}
and thus,
\begin{equation}
\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
\end{equation}

They referred this to as the MinT solution. The loss function they considered is equivalent to the Mahalanobis distance between $\hat{\bm{y}}_{T+h}$ and $\tilde{\bm{y}}_{T+h}$. i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>_{\bm{W}_h}$.

@@

For probabilistic forecasts, reconciliation implies finding the probability measure of the coherent forecasts using the information from an incoherent probabilistic forecast measure. A more formal definition is given below.

\begin{definition} \label{def:reconprob}
  Suppose $(\mathbb{R}^n, \mathscr{F}^n, \hat{\nu})$ is an incoherent probability triple and $(\mathbb{R}^m, \mathscr{F}^m, \nu^m)$ is a probability triple defined on $\mathbb{R}^m$. Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $. Then the probability measure on the reconciled bottom levels is such that
  \begin{equation}
  \nu^m(\bm{A}) = \hat{\nu}(\bm{g}^{-1}(\bm{A})), \quad \forall \quad \bm{A} \in \mathscr{F}^m.
  \end{equation}
  Further the probability measure of the whole reconciled hierarchy is given by
  \begin{equation}
  \tilde{\nu}(\bm{S}(\bm{A})) = \hat{\nu}(\bm{g}^{-1}(\bm{A})) \qquad \forall \bm{A} \in \mathscr{F}^m,
  \end{equation}
  where $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{C}^m$ and $\tilde{\nu}(\cdot)$ is the probability measure on the measure space $(\mathbb{C}^m, \mathscr{F}_S)$.
\end{definition}

We now discuss how this definition can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.

Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$ are given by \eqref{4.3}. Suppose $\hat{\bm{f}}(\cdot)$ is the probability density of $\hat{\bm{y}}_{t+h}$. Our goal is to reconcile $\hat{\bm{f}}(\cdot)$ such that the density lives on $\mathbb{C}^m$. In order to obtain this reconciled density, we need to project $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ onto $\mathbb{C}^m$ along the direction of $\mathbb{N}^{n-m}$.

Let the density of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ be denoted by $\bm{f_B}(\cdot)$. Then it follows from  \eqref{4.3}, and standard results for densities of transformed variables, that
\begin{equation}\label{4.5}
\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \,\Big|\bm{S} ~ \vdots~ \bm{R}\Big|,
\end{equation}
where $|\cdot|$ denotes the determinant of a matrix. Now that we have the density of $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating \eqref{4.5} over the range of $\tilde{\bm{t}}_{t+h}$. This will result in the reconciled density of the bottom level series $\tilde{\bm{b}}_{t+h}$,
\begin{equation}\label{4.6}
\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{\lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h})\,  \Big|\bm{S} ~ \vdots~ \bm{R}\Big| \, d\tilde{\bm{t}}_{t+h}.
\end{equation}

Finally to get the reconciled density of the whole hierarchy, we simply follow Definition \ref{def:cohprob} to obtain
\begin{equation}\label{4.7}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\bm{S}\circ \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h}).
\end{equation}
This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the space $\mathbb{C}^m<\mathbb{R}^n$. The following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.

@@

Suppose $\mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \overset{d}{\leftrightarrow} \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$. Then from \eqref{4.5} it follows that

@@

\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \, \Big|\bm{S} ~ \vdots~ \bm{R}\Big| = \frac{\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) }{\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1}\Big|}.

@@

By substituting the Gaussian distribution function for $\bm{f_B}(\cdot)$ we get

@@

\bm{f_B}(\cdot)

@@

\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})' \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1}\Big|},\\

@@

\frac{\exp\left\{-\frac{1}{2}\Big((\bm{S} ~ \vdots~ \bm{R})\bt-\bm{\hat{\mu}}_{t+h}\Big)' \bm{\hat{\Sigma}_{t+h}}^{-1}\Big((\bm{S} ~ \vdots~ \bm{R})\bt-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1}\Big|},\\

@@

\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1} \Big|}
\exp \Big\{-\frac{1}{2}\Big(\bt-(\bm{S} ~ \vdots~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\Big)'\\
& \hspace*{6cm} \Big[(\bm{S} ~ \vdots~ \bm{R})\bm{\hat{\Sigma}_{t+h}}(\bm{S} ~ \vdots~ \bm{R})'\Big]^{-1}
\Big(\bt-(\bm{S} ~ \vdots~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.

@@

Recall that

@@

(\bm{S} ~ \vdots~ \bm{R})^{-1} =

@@

where $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{Q}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then

@@

\bm{f_B}(\cdot)& =\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\PQ \Big|}
\exp \Big\{-\frac{1}{2}\Big[\bt-\PQ\bm{\hat{\mu}}_{t+h}\Big]'\\[-0.5cm]
& \hspace*{7cm}
\Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big]^{-1}\Big[\bt-\PQ\bm{\hat{\mu}}_{t+h}\Big] \Big\},\\[0.5cm]
